---
title: "Assignment 5-B"
subtitle: "Version 1.0.0"
output: github_document
author: Tianyi Zheng
---

## Overview

+ **Option A:** Strings Regex

## Option A -- Strings in R

### Exercise 1 (9 points)

Load the packages.
```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
```

Here we look into Jane Austen’s 6 books and transform it into tidytext format.
Then convert the tidytext to lower cases and also remove any stop words. 
```{r}
   (JAtidy<-austen_books() %>%
   group_by(book) %>%
   unnest_tokens(word, text) %>% 
   anti_join(stop_words) %>% 
   ungroup())
```

We visualize the word count from the 6 books by a bar chart, and filter by word count above 600 to get the most common words.
```{r}
JAtidy %>% 
  count(word, sort = TRUE) %>% 
  filter(n > 600) %>% 
  ggplot(aes(n,reorder(word,n)))+
  geom_col() +
  ylab("Word")+
  xlab("Count")+
  theme_classic()
```


### Exercise 2 (9 points)

Load the testing package.
```{r}
library(testthat)
```
#### 2.1 Documentation and Design
**Description**

This function takes a string(char) or an atomic vector of strings(char) and translate it into the Minions language. Specifically, there are 6 rules:

1. If the word start with a vowel letter, move the vowel letter to the end and add "nana" to it.

2. If the word start with "T" or "H", convert it to a "B" and add "la" at the end.

3. If the word start with at least 2 vowel letters in the first 3 letters (can be YNY, YYN, NYY, YYY), move all 3 letters to the end and add "lalala" to the end.

4. If the word is "banana"(not case-sensitive), convert it to "BA-NA-NA!"

5. Since the translation is designed for words only, any non-letter characters (numbers, symbols...) will be ignored.

6. If none of the above rules apply, return the original word.

**Input (Arguments)**

- `data`: a string(char) or an atomic vector of strings(char).
  - _Justification_: Since the function is translating, only character would make sense, so the acceptable datatype is character, which can be a single word or an atomic vector of words. Lists are not supported by the function because it would need to iterate through each element to validate the datatype, which is not performance-wise.

  
**Output**

A string(char) or an atomic vector of strings(char) that translated into the Minions language.

  - _Justification_: Since the functionality is only translating, the datatype is not expected to be changed.

#### 2.2 Function
This is a helper function that applies rules to a single word(char).
```{r}
MinionsTranslatorSingle<-function(data){
  data<-tolower(data)
  
  if(length(data)==1){
    if(tolower(data)=="banana"){
      return("BA-NA-NA!")
    }
    if(length((str_subset(data,"^[Tt]|^[Hh]")))>0)
       {
         return(paste0("b",str_sub(data, start=2),"la"))
    }
    if(length((str_subset(data,"^[A-z][aeiouAEIOU][aeiouAEIOU]|^[aeiouAEIOU][A-z][aeiouAEIOU]|^[aeiouAEIOU][aeiouAEIOU][A-z]|^[aeiouAEIOU][aeiouAEIOU][aeiouAEIOU]")))>0)
    {
      return(paste0(str_sub(data, start=4),str_sub(data, start=1, end=3),"lalala"))
    }
    if(length((str_subset(data,"^[aeiouAEIOU]")))>0)
    {
      return(paste0(str_sub(data, start=2),str_sub(data, start=1, end=1),"nana"))
    }
    
    else{
    data
    }
  }
}
```

This is the main function.
```{r}
MinionsTranslator<-function(data){
  if(typeof(data)!="character"){
    stop('The function expect input data as character\n',
         'but the input is: ', typeof(data)[1])
  }
  
  data<-tolower(str_remove_all(data,"[^A-z]"))
  
  map_chr(data,MinionsTranslatorSingle)

}
```


#### 2.3 Test the Function 
Examples:
```{r}
MinionsTranslator("banana")
MinionsTranslator(c("Apple","austin","Canada"))
```

3 tests on unexpected input types, main function output and helper function outpout.

```{r}
test_that("Unexpected Input Testing",{
expect_error(MinionsTranslator(list("abc","bcd")))
expect_error(MinionsTranslator(1))
expect_error(MinionsTranslator(NULL))
})

test_that("Output check",{
expect_equal(MinionsTranslator(c("obvious","area","banana")),c("bviousonana", "aarelalala", "BA-NA-NA!"))
expect_equal(MinionsTranslator(c("obvi@us","1a2b3c4d")),c("bviusonana", "bcdanana"))
})

test_that("Helper Function Testing",{
expect_equal(MinionsTranslatorSingle("orange"),"ngeoralalala")
expect_equal(MinionsTranslatorSingle("Alien"), "enalilalala")
expect_equal(MinionsTranslatorSingle("why"),"why")
expect_equal(MinionsTranslatorSingle("Zoo"),"zoolalala")
})

```
