---
title: "Assignment 1-B"
subtitle: "Version 1.0" 
output: github_document
author: Tianyi Zheng
---

Loading Packages
```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(gapminder)
library(testthat)
library(broom)
```


## Exercise 1: Functions (10 points)

### 1.1 Documentation and Design (5)
<!----------- Documentation goes here ---------------------->

**Description**

This function takes a dataset(as a list, and dataframes/tibbles are lists) of two quantitative variables and fits a single linear regression model from them, then it displays a scatterplot with fitted regression line. Also, it displays any influential points as red color based on user defined criteria (cut-off for cook's distance).

**Input (Arguments)**

- `data`: a list (dataframe, tibble, etc...) with two quantitative variables.
  - _Justification_: Data means the data that would be used to fit the model and made the plot. There is no default value of data. 
- `xy`: logicals. If TRUE then the first column of the list would assumed to be the independent variable, and vice versa for FALSE. The default if TRUE.
  - _Justification_: xy means the first column is the independent variable (x) in the regression model, and the second column is the dependent variable (y). The default is TRUE, which is consistent with 'xy'. 
- `cooksd`: a non-negative numerical value for cook's distance threshold. The default is 0.5.
  - _Justification_: Cooksd means the Cook's Distance for identifying influential observations. Empirically, a cook's distance above 0.5 would need to be examined, so the default is 0.5.
- `outputcount`: logicals. If TRUE then print a message on the count of influential observations.
  - _Justification_: Outputcount means print out the count of influential observations, and it is safer to not printing when user did not specify.
- `verbose`: logicals. If TRUE then print a message to inform the user that the process is running.
  - _Justification_: Verbose is a widely accepted terminology for including message feedback, and it is safer to not include when user did not specify.
- `...`: additional arguments to be passed to the low level regression fitting functions. 
  - _Justification_: The ellipsis allows for more generalizability.

**Output**

A ggplot object(scatterplot) with fitted regression line and red labelled influential points. 

  - _Justification_: The purpose of this function is to create a data visualization to indicate influential observations in linear bivariate analysis.

<!---------------------------------------------------------->

### 1.2 Write the Function (3)
<!------------ Write your function below here -------------->
Error Messages Justification:
Data needs to be a list of two quantitative  variables in order to fit linear regression model and create scatter plot.
Xy needs a non-negative number, and cooksd,outputcount,verbose needs to be boolean.
The process would not make sense with unexpected inputs, therefore it should stop.

```{r}
scatterinfobs<-function(data, xy=TRUE, cooksd=0.5, outputcount=FALSE, verbose=FALSE,...){
  if(typeof(data)!="list"){
    stop('The function expect input data as list\n',
         'but the input is: ', typeof(data)[1])
  }
  if(ncol(data)!=2){
    stop('The function expect two columns\n',
         'but the input has: ', ncol(data))
  }
  if(!is.numeric(data[[1]])|!is.numeric(data[[2]])){
    stop('The function expect quantinative/numberic variables.')
  }
  if(!is.numeric(cooksd)|cooksd<0){
    stop('cooksd needs to be a non-negative number')
  }
  if(!is.logical(xy)){
    stop('xy needs to be a boolean value')
  }
  if(!is.logical(outputcount)){
    stop('outputcount needs to be a boolean value')
  }
  if(!is.logical(verbose)){
    stop('verbose needs to be a boolean value')
  }  
  if(xy==TRUE){
    x=data[[1]]
    y=data[[2]]
    xname=colnames(data)[1]
    yname=colnames(data)[2]
   
  }
  if(xy==FALSE){
    x=data[[2]]
    y=data[[1]]
    xname=colnames(data)[2]
    yname=colnames(data)[1]
   
  }
 model<-lm(y~x,...)
 if(verbose==TRUE){
   cat("Linear model fitting done, now creating plot...")
 }
 
 if(outputcount==TRUE){
   Infobvec<-as.vector(cooks.distance(model)>cooksd)
   Infobnum<-length(subset(Infobvec,Infobvec==TRUE))
   cat("We have",Infobnum,"influential observations","at",cooksd,"cook's distance threshold")
 }
data %>% 
  mutate(Infob=cooks.distance(model)>cooksd) %>% 
  ggplot(aes(x,y))+
  geom_point(aes(color=Infob))+
  geom_smooth(method=lm, se=FALSE)+
  scale_color_manual(values=c("Black", "Red"))+ 
  theme_bw()+
  labs(x=xname,y=yname)+
  theme(legend.position = "none")
}
```
<!---------------------------------------------------------->



### 1.3 Test the Function (2 points)

<!------------ Test your function below here --------------->
```{r}
scatterinfobs(gapminder %>% 
                select(lifeExp,pop))
scatterinfobs(gapminder %>% 
                select(pop,lifeExp),xy=FALSE,cooksd=0.05,verbose = TRUE,outputcount = TRUE)
scatterinfobs(gapminder %>% 
                select(lifeExp,gdpPercap),cooksd = 0.05)
```

```{r}
test_that("Unexpected Input Testing",{
expect_error(scatterinfobs(data=gapminder %>% 
                select(country,pop)))
expect_error(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop),xy=1))
expect_error(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop),verbose ="TRUE"))
expect_error(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop),outputcount = 0))
expect_error(scatterinfobs(data=gapminder %>% 
                select(year,country,pop)))
expect_error(scatterinfobs(data=FALSE))
expect_error(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop),cooksd = "0.5"))
  
})

test_that("Output check",{
expect_equal(class(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop))),c("gg","ggplot"))
expect_output(scatterinfobs(data=gapminder %>% 
                select(gdpPercap,pop),outputcount = TRUE))
})

```

<!---------------------------------------------------------->


## Exercise 2: List Columns (8 points)

### 2.1 (8 points) 
<!------------ Put your work here -------------------------->
Check Gapminder Dataset
```{r}
head(gapminder)
```

1. Create linear regression model column for each continent, to regress lifeExp and pop on gdpPercap
```{r}
(gdpmodelPerContinent<-gapminder %>% 
  select(continent,lifeExp,pop,gdpPercap) %>% 
  nest(data=c(lifeExp,pop,gdpPercap)) %>% 
  mutate(model= map(data, ~{
    lm(gdpPercap~lifeExp+pop,data = .x)
  })))
  
```
2. Evaluate the model by getting the linear model coefficient into its separate column
```{r}
gdpCoef<-gdpmodelPerContinent %>% 
  mutate(coef= map(model, tidy))
```
3. Print out the tibble so far.
```{r}
gdpCoef
```
4. Unnest the coef column, and only keep relevant columns and the statistically significant (p-value less than 0.05) non-intercept terms.
```{r}
gdpCoef %>% 
  unnest(coef) %>% 
  select(continent,model,term,p.value) %>% 
  filter(p.value<0.05) %>% 
  filter(term!="(Intercept)") 
```
5.Brief explanation:
The final tibble in 4 shows the linear regression model (in the model column) result that regress lifeExp(life expectancy) and pop(population) on gdpPercap (GDP per capita) per continent. The final tibble only kept statistically significant (p-value less than 0.05 in p.value column) non-intercept terms (in the term column).
<!---------------------------------------------------------->


### 2.2 (**Optional**, 1 bonus point)

Here, we still fit the model in the previous part, which regress lifeExp(life expectancy) and pop(population) on gdpPercap (GDP per capita). From the cook's distance plot, we can identify that record 853,854,857 are influential observations. After looking up, those records belong to Kuwait.
Kuwait is an interesting country in this case because although it is not the country with highest life expectancy or population, it has the highest GDP per capita, in fact, more than twice for any other countries in the gapminder dataset.
```{r}
model<-lm(gdpPercap~lifeExp+pop,data=gapminder)
plot(model)
gapminder[c(853,854,857),]
gapminder %>% 
  group_by(country) %>% 
  summarise(lifeExp=mean(lifeExp),pop=mean(pop),gdpPercap=mean(gdpPercap)) %>% 
  arrange(desc(gdpPercap))
```
